Honey Bees - DESeq

### 2018-04-09 VirusHoneyBee/DESeq2/Method1/makeDataMetrics.Rmd
Examine overlap between Galbraith supplemental DEGs and our DESEq DEGs of their data

for (i in 1:(length(uTreat)-1)){
  for (j in (i+1):length(uTreat)){
    res <- results(dds, contrast=c("treatment",uTreat[i],uTreat[j]))
    hist(res$pvalue, breaks=20, col="grey", main=paste("pvalue for", uTreat[i], "and", uTreat[j]))
    degLength <- length(which((res@listData)$padj <0.05))
    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength))

    metrics = as.data.frame(res@listData)
    metrics = cbind(ID = res@rownames, metrics)
    metrics$ID = as.character(metrics$ID)
    dataMetrics[[paste0(uTreat[i], "_", uTreat[j])]] <- metrics
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(dataMetrics, file="dataMetrics.Rds")
```

>>>>

for (i in 1:(length(uTreat)-1)){
  for (j in (i+1):length(uTreat)){
    res <- results(dds, contrast=c("treatment",uTreat[i],uTreat[j]))
    hist(res$pvalue, breaks=20, col="grey", main=paste("pvalue for", uTreat[i], "and", uTreat[j]))
    degLength <- length(which((res@listData)$padj <0.05))

    metrics = as.data.frame(res@listData)
    metrics = cbind(ID = res@rownames, metrics)
    metrics$ID = as.character(metrics$ID)
    dataMetrics[[paste0(uTreat[i], "_", uTreat[j])]] <- metrics

    t1Length <- length(which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0))
    t2Length <- length(which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0))

    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength, Treatment1Larger = t1Length, Treatment2Larger = t2Length))
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(dataMetrics, file="dataMetrics.Rds")
```
